Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-05-01 paper.tex
Add final section outline and figs

>>>>

\section{Matching MIDI Files to the MSD}
\label{sec:msd}

Given trained networks, we hash the entire MSD and all MIDIs.
For each MIDI, we compute the DTW distance in the same way as above except that gully = .9 and penalty = 4 and we don't normalize by sim mtx mean.
Because we already matched and aligned, we can look at the rank of the correct match.
We can compute the proportion of matches below a given rank threshold: 1, 13.3\%; 10, 42.3\%, 100, 64.4\%; 1000, 83.3\% - show a plot of this.
We can't solely rely on hash matching, but it can prune out order of magnitude of possibilities with a small loss in accuracy.
We can compute the mean reciprocal rank - .2314.
Most errors caused by incorrect tempo match - show plot of rank vs score with color corresponding to whether the tempo matched.
Speedup: sim mtx is 50-300x faster, DTW is 4-15x faster.
Result: Matching a single MIDI against the MSD takes a few minutes instead of a few hours; parallelized, we are able to match our entire MIDI dataset in 20 days.
Future work: Pruning DTW calculations.

\begin{figure}[h!]
  \label{fig:percent_below_rank}
  \centering
    \includegraphics[width=0.5\textwidth]{percent_below_rank.png}
  \caption{Percentage of hash matches below rank}
\end{figure}

\begin{figure}[h!]
  \label{fig:rank_vs_score}
  \centering
    \includegraphics[width=0.5\textwidth]{rank_vs_score.png}
  \caption{Hash match rank vs. DTW score with color corresponding to correct tempo}
\end{figure}
